Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-07-15 tex/test-WW-type-00y-PS.tex
text

%Editing commands
\newcommand{\TD}{{\bf TODO:}}
\newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}

\definecolor{darkgreen}{rgb}{0,0.65,0}
\definecolor{orange}{rgb}{1,0.4,0.1}
\newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
\newcommand{\orange}[1]{{\color{orange} #1}}
\newcommand{\ps}[1]{\blue{ #1}}
\newcommand{\ak}[1]{\orange{ #1}}
\newcommand{\ms}[1]{\darkgreen{ #1}}

@@

\preprint{\red{version ``00x''}; JLAB-THY-18-XXXX}
%\preprint{version 00x-PS}

@@

\abstract{
We present the complete cross-section 
for the production of unpolarized hadrons in semi-inclusive
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
the Wandzura--Wilczek-type approximation \ps{which consists in systematically
assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering,
	transverse momentum dependent distribution and fragmentation 
	functions, spin and azimuthal asymmetries, leading and subleading twist}

@@

\vspace{1cm}

@@

General comments: 
	\red{red color, command: {$\backslash{\rm red}\{\dots\}$}}\\
Alexei's corrections: 
	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
Aram's corrections: 
	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
Marc's corrections: 
	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
Peter's corrections: 
	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
Anatoli Vasilievich, Bakur, Bernie, Gunar, Kemal, Saman: \\
	corrections already introduced in black color \& confirmed by e-mail.

@@

One powerful tool to study TMDs are measurements of the 
semi-inclusive deep-inelastic scattering (SIDIS) process.
By exploring various possibilities for the lepton beam and target 
polarizations\footnote{\ps{It is important to stress that this
	information could not have been obtained without advances 
	in target polarization techniques employed in the HERMES, 
	COMPASS and JLab experiments 
	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.}}
unambiguous information can be accessed on the 8 leading--twist 
TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
linear combinations of the 16 subleading--twist TMDs 
\cite{Goeke:2005hb,Bacchetta:2006tn}.
Complementary information can be obtained 
from the Drell-Yan process \cite{Arnold:2008kf}, 
and $e^+e^-$ annihilation \cite{Metz:2016swz}.

In QCD the TMDs are independent functions. Each TMD contains unique
information on a different aspect of the nucleon structure. 
Twist-2 TMDs have partonic interpretations. Twist-3 TMDs 
give insights on quark-gluon correlations in the nucleon
\cite{Miller:2007ae,Burkardt:2007rv,Burkardt:2009rf}. 
Besides positivity constraints \cite{Bacchetta:1999kz} 
there is little model-independent information on TMDs. 
An important question with practical applications is:
do useful {\sl approximations} for TMDs exist? 
Experience from collinear PDFs encourages to explore this possibility: 
the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
terms \cite{Wandzura:1977qf,Jaffe:1991ra}
\ms{(the index $a=q\,,\bar q$ does not include gluons for
$h_1^a$, $h_L^a$ and other chiral odd TMDs below)}.
We shall refer to the latter generically as $\bar{q}gq$--terms, keeping in 
mind one deals in each case with matrix elements of different operators.
The $\bar{q}gq$--correlations contain new insights on hadron structure 
which are worthwhile exploring for their own sake, 
see \cite{Jaffe:1989xx} on $g_T^a(x)$.

@@

The present work is the first study of all SIDIS structure functions up to 
twist-3 in a unique approach. Our results are of importance for experiments 
prepared in the near-term at Jefferson Lab (JLab) with 12$\,$GeV beam energy
upgrade and COMPASS or proposed in the long-term (Electron Ion Collider), 
and provide helpful input for Monte Carlo event generators 
\cite{Avakian:2015vha}.

Our predictions will either be confirmed within the expected accuracy
or will not not supported by data. In either case our work will provide
a useful benchmark, and either call for dedicated theoretical 
studies to explain either the pertinent $\bar{q}gq$--terms are 
so small or why they are so sizable. In either case our results will 
deepen the understanding of  $\bar{q}gq$--correlations, \ps{pave the 
way towards testing} the validity of the TMD factorization approach 
at subleading twist, and help us to guide further developments.

In this work, after introducing the SIDIS process and defining TMDs and 
FFs (Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
approximations, and review what is presently known about them 
from experiment and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations 
all leading and subleading SIDIS structure functions are described in terms of 
a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
and review how these basis functions describe available data 
(Sec.~\ref{Sec-5:twist-2+basis}).
We will systematically apply the WW and/or WW-type approximations
to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
The Appendices \ref{App:basis} and \ref{App:factor} contain 
technical details. \AP{In App.~C we describe an open source 
package publicly available on \texttt{github.com}\footnote{\href{%
	https://github.com/prokudin/WW-SIDIS}{
	https://github.com/prokudin/WW-SIDIS}} 
	implemented in \texttt{mathematica}~\cite{Mathematica} 
	(already available) and \texttt{Python} 
	(to be released in the near future).}

@@

The SIDIS process  $lN\to l^\prime h X$ is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
Note that we consider the production of unpolarized hadrons in DIS of 
charged leptons (electrons, positrons, muons) at $Q^2 \ll M_Z^2$ 
in the single photon exchange approximation.
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum. 
In principle the cross section is also differential with respect to the
azimuthal angle $\psi_l$ characterizing the overall orientation of the 
lepton scattering plane in a fixed lab frame. \ak{The origin of this 
angle can be chosen arbitrarily. For a transversely polarized target 
it is convenient to choose the origin of the angle $\psi_l$ in the 
direction of $\vec{S}_T$.}
It is convenient to define the unpolarized 
lepton--quark scattering subprocess cross section
\ba\label{Eq:sigma0-FUU}
	\frac{d \hat{\sigma}}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

@@

The connection of ``collinear'' SIDIS structure functions
in (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
to those known from inclusive DIS is established by integrating over $z$
and summing over hadrons as 
\begin{subequations}\begin{alignat}{4}
	&\sum\limits_h\int d z\;z\;F_{UU}(x,z) 
	&\equiv	&&	& 2\,x\,F_1(x) \;, 
	\label{Eq:DIS-F1}\\ % x\sum_q e_q^2\,f_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LL}(x,z) 
	&\equiv && 	& 2\,x\,g_1(x) \;, 
	\label{Eq:DIS-g1}\\ % x\sum_q e_q^2\,g_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LT}^{\cos\phi_S}(x,z) \;\;
	&\equiv && \;\; -\,\gamma\; & 2\,x\biggl(g_1(x)+g_2(x)\biggr) \;, 
	\label{Eq:DIS-gT}\\ % -\,\frac{2M_Nx^2}{Q} \sum_q e_q^2\,g_T^q(x) 
	&\sum\limits_h\int d z\;z\;F_{UT}^{\sin\phi_S}(x,z) 
	&=      && 	    & \;\; 0 \, ,
	\label{Eq:DIS-zero}
\end{alignat}\end{subequations}
where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time reversal
symmetry of strong interactions, and \ak{terms suppressed by $1/Q^2$ are 
consequently neglected troughout this work including the twist-4 DIS 
structure function $F_L(x)$. }

@@

$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. \ms{The 

@@

Sec.~\ref{Sec-3.2:WW-type-TMD-FF}.} The weight functions are defined as

@@

Before introducing the WW-type approximations in the next section, 
\ms{we would like to add a comment on TMD factorization: the 
partonic description of the leading-twist structure functions in 
(\ref{Eqs:structure-functions-twist-2}) is based on factorization 
theorems \cite{Collins:1981uk,Ji:2004wu,Ji:2004xq,Collins:2011zzd,
Echevarria:2012js}. In contrast to this, the partonic description 
of the subleading-twist structure functions in 
(\ref{Eqs:structure-functions-twist-3}) is based on the
{\it assumption} that that SIDIS cross section factorizes.

In fact, a lot of progress has been achieved in recent years in the 
theoretical understanding of leading twist observables within the TMD 
framework --- including definition, renormalization and evolution of 
leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
In contrast to this, the theory for subleading-twist TMD observables is 
only pourly developed. Still to the present day, the state-of-the-art 
approach to subleading twist TMD observables is the one of 
Refs.~\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
Bacchetta:2006tn}, 
based on a TMD tree-level formalism which we adopt here.
In fact, the results of Refs.~\cite{Metz:2004je,Gamberg:2006ru}
indicate doubts even in the tree-level formalism. 
Recently, an attempt was made to remedy these doubts \cite{Chen:2016hgw}.
Keeping in mind these ``words of warning,'' still the formulas 
(\ref{Eqs:structure-functions-twist-3}) 
are the best that theory has to offer currently. We may consider 
(\ref{Eqs:structure-functions-twist-3}) as a model itself for 
the twist-3 SIDIS observables. We hope that the phenomenological 
approach based on WW-type approximations pursued in this work might 
lead to more insight into these observables, and eventually might 
trigger more theory efforts in the future.
}

@@

\ms{The relations (\ref{Eq:WW-original1}--\ref{Eq:WW-original-e})
have been derived basically using operator product expansion
techniques \cite{Wandzura:1977qf,Jaffe:1991ra}. Notice that the 
operators defining $g_T^a$ and and $h_L^a$ can also be decomposed 
within the TMD framework by means of a combination of relations 
derived from the QCD equations of motion and further 
constraint relations, called Lorentz-Invariance Relations (LIRs), 
(see recent review \cite{Kanazawa:2015ajw} and references therein) 
into a twist-2 part, and dynamical twist-3 (interactions dependent) 
$\bar{q}gq$-terms and current quark mass terms.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.48\textwidth]{\FigPath/g2.pdf} 
\includegraphics[width=0.48\textwidth]{\FigPath/g2-HERMES.pdf} 
\caption{\label{Fig:g2} 
The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets. 
Left panel: data from E144 and E155 experiments at 
$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. 
Right panel: HERMES data \ps{for $Q^2>1\,{\rm GeV}^2$ with}
$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
The estimate of the theoretical uncertainty is described in the text.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We present calculations of $g_2(x)_{\rm WW}$ in Fig.~\ref{Fig:g2}.
\ps{This result is obtained using the LO $g_1^a(x)$-parametrization 
\cite{Gluck:1998xa}. In order to display the theoretical ``uncertainty 
band'' of this WW-approximation of about $40\,\%$ as deduced in 
Ref.~\cite{Accardi:2009au} we proceed as follows: we split the 
$40\,\%$ uncertainty} in two parts, $\varepsilon_1=\pm 20\,\%$ and 
$\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
and estimate the impact of this uncertainty as 
\be\label{Eq:g2-in-WW-model-violation}
    g_2(x)_{\rm WW} = (1\pm\varepsilon_1)\frac{ d\;}{ d x}\;\Biggl[
    x\int_x^1\frac{ d y}{y} \,\biggl(
    \frac12\sum_ae_a^2\,g_1^a(y(1\pm\varepsilon_2))\biggr)\Biggr]\,.
\ee
The effect of $\varepsilon_1$ is to change the magnitude
of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
the highest measured $x$--bin.
The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
and in line with theory predictions \cite{Balla:1997hf}.
Our estimate with the splitted uncertainties 
$\varepsilon_{1,2}$ may overestimate in certain $x$--bins the 
$40\,\%$--``uncertainty band'' estimated in \cite{Accardi:2009au}. 
This however helps us to display a conservative estimate of possible 
uncertainties. 
We conclude that the WW--approximation works reasonably well, 
see Fig.~\ref{Fig:g2}.

@@

For the time being, we content ourselves with rather crude comparisons 
based on the \ak{lattice data}
published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
These early works explored all nucleon and quark polarizations, but 
they used a gauge link that does not incorporate the final or initial 
state interactions present in SIDIS or Drell-Yan experiments. In other 
words, the transverse momentum dependent quantities computed in
\cite{Hagler:2009mb,Musch:2010ka} are not precisely the TMDs measurable 
in experiment. More caveats will be discussed along the way.

@@

	\stackrel{\text{Gaussian}}{=} -c_{7,q}\\

@@

	\stackrel{\text{Gaussian}}{=} -c_{10,q}

@@

To summarize, our procedure is to solve first the convolution 
integrals in Gauss Ansatz, and use then WW-type approximations.
When implementing this procedure we will see that the results 
for the structure functions can be conveniently expressed in 
terms of the basis TMDs or their adequate transverse moments.

@@

}

>>>>

%Editing commands
\newcommand{\TD}[1]{{{\bf TODO:} \color[rgb]{0.65,0,0.15} #1}}
\newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}

\definecolor{darkgreen}{rgb}{0,0.65,0}
\definecolor{orange}{rgb}{1,0.4,0.1}
\newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
\newcommand{\orange}[1]{{\color{orange}#1}}

\newcommand{\ak}[1]{\orange{#1}}
\newcommand{\ps}[1]{\blue{#1}}
\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
\newcommand{\ms}[1]{\darkgreen{#1}}
\newcommand{\kt}[1]{{\color[rgb]{0.1,0.5,0}#1}}

@@

\preprint{\red{version ``00y''}; JLAB-THY-18-XXXX}

@@

\abstract{
We present the complete cross-section 
for the production of unpolarized hadrons in semi-inclusive
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
the Wandzura--Wilczek-type approximation which consists in systematically
assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering,
	transverse momentum dependent distribution and fragmentation 
	functions, spin and azimuthal asymmetries, leading and subleading twist}

@@

@@

General comments: 
	\TD{dark red color, command: {$\backslash{\rm TD}\{\dots\}$}}\\
Alexei's corrections: 
	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
Aram's corrections: 
	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
Gunar's corrections: 
	\gs{violett color, command: {$\backslash{\rm gs}\{\dots\}$}}\\
Kemal's corrections: 
	\kt{greenish color, command: {$\backslash{\rm kt}\{\dots\}$}}\\
Marc's corrections: 
	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
Peter's corrections: 
	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
Anatoli Vasilievich, Bakur, Bernie, Saman: \\
	corrections already introduced in black color \& confirmed by e-mail.

@@

One powerful tool to study TMDs are measurements of the 
semi-inclusive deep-inelastic scattering (SIDIS) process.
By exploring various possibilities for the lepton beam and target 
polarizations unambiguous information can be accessed on the 8 leading--twist 
TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
linear combinations of the 16 subleading--twist TMDs 
\cite{Goeke:2005hb,Bacchetta:2006tn}.
	It is important to stress that this information could not have 
	been obtained without advances in target polarization techniques 
	employed in the HERMES, COMPASS and JLab experiments 
	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.
Complementary information can be obtained 
from the Drell-Yan process \cite{Arnold:2008kf}, 
and $e^+e^-$ annihilation \cite{Metz:2016swz}.

In QCD the TMDs are independent functions. Each TMD contains unique
information on a different aspect of the nucleon structure. 
Twist-2 TMDs have partonic interpretations. Twist-3 TMDs 
give insights on quark-gluon correlations in the nucleon
\cite{Miller:2007ae,Burkardt:2007rv,Burkardt:2009rf}. 
Besides positivity constraints \cite{Bacchetta:1999kz} 
there is little model-independent information on TMDs. 
An important question with practical applications is:
do useful {\sl approximations} for TMDs exist? 
Experience from collinear PDFs encourages to explore this possibility: 
the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
terms \cite{Wandzura:1977qf,Jaffe:1991ra}
(the index $a=q\,,\bar q$ does not include gluons for
$h_1^a$, $h_L^a$ and other chiral odd TMDs below).
We shall refer to the latter generically as $\bar{q}gq$--terms, keeping in 
mind one deals in each case with matrix elements of different operators.
The $\bar{q}gq$--correlations contain new insights on hadron structure 
which are worthwhile exploring for their own sake, 
see \cite{Jaffe:1989xx} on $g_T^a(x)$.

@@

The present work is the first study of all SIDIS structure functions up to 
twist-3 in a unique approach. Our results are of importance for experiments 
prepared in the near-term at Jefferson Lab (JLab) with 12$\,$GeV beam energy
upgrade and COMPASS or proposed in the long-term (Electron Ion Collider), 
and provide helpful input for the development of Monte Carlo event generators 
\cite{Avakian:2015vha}.

Our predictions will either be confirmed within the expected accuracy
or will not be supported by data. In either case our work will provide
a useful benchmark, and call for dedicated theoretical 
studies to explain (i) why the pertinent $\bar{q}gq$--terms are 
small or (ii) why they are sizable. In either case our results will 
deepen the understanding of  $\bar{q}gq$--correlations, pave the 
way towards testing the validity of the TMD factorization approach 
at subleading twist, and help us to guide further developments.

In this work, after introducing the SIDIS process and defining TMDs and 
FFs (Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
approximations, and review what is presently known about them 
from experiment and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations 
all leading and subleading SIDIS structure functions are described in terms of 
a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
and review how these basis functions describe available data 
(Sec.~\ref{Sec-5:twist-2+basis}).
We will systematically apply the WW and/or WW-type approximations
to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
The Appendices \ref{App:basis} and \ref{App:factor} contain 
technical details. 
	In App.~C we describe an open source 
	package publicly available on \texttt{github.com}\footnote{\href{%
	https://github.com/prokudin/WW-SIDIS}{
	https://github.com/prokudin/WW-SIDIS}} 
	implemented in \texttt{mathematica}~\cite{Mathematica} 
	(already available) and \texttt{Python} 
	(to be released in the near future).

@@

The SIDIS process  $lN\to l^\prime h X$ is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, $l^\prime$ and $P_h$ are the momenta of the outgoing
lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects the z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
Note that we consider the production of unpolarized hadrons in DIS of 
charged leptons (electrons, positrons, muons) at $Q^2 \ll M_Z^2$ 
in the single photon exchange approximation.
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum. 
In principle the cross section is also differential with respect to the
azimuthal angle $\psi_l$ characterizing the overall orientation of the 
lepton scattering plane in a fixed lab frame. The origin of this 
angle can be chosen arbitrarily. For a transversely polarized target 
it is convenient to choose the origin of the angle $\psi_l$ in the 
direction of $\vec{S}_T$.
It is convenient to define the unpolarized 
lepton--quark scattering subprocess cross section
\ba\label{Eq:sigma0-FUU}
	\frac{d \hat{\sigma}}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

@@

The connection of ``collinear'' SIDIS structure functions
in (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
to those known from inclusive DIS is established by integrating over $z$
and summing over hadrons as 
\begin{subequations}\begin{alignat}{4}
	&\sum\limits_h\int d z\;z\;F_{UU}(x,z) 
	&\equiv	&&	& 2\,x\,F_1(x) \;, 
	\label{Eq:DIS-F1}\\ % x\sum_q e_q^2\,f_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LL}(x,z) 
	&\equiv && 	& 2\,x\,g_1(x) \;, 
	\label{Eq:DIS-g1}\\ % x\sum_q e_q^2\,g_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LT}^{\cos\phi_S}(x,z) \;\;
	&\equiv && \;\; -\,\gamma\; & 2\,x\biggl(g_1(x)+g_2(x)\biggr) \;, 
	\label{Eq:DIS-gT}\\ % -\,\frac{2M_Nx^2}{Q} \sum_q e_q^2\,g_T^q(x) 
	&\sum\limits_h\int d z\;z\;F_{UT}^{\sin\phi_S}(x,z) 
	&=      && 	    & \;\; 0 \, ,
	\label{Eq:DIS-zero}
\end{alignat}\end{subequations}
where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time reversal
symmetry of strong interactions, and terms suppressed by $1/Q^2$ are 
consequently neglected troughout this work including the twist-4 DIS 
structure function $F_L(x)$.

@@

$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. The 

@@

Sec.~\ref{Sec-3.2:WW-type-TMD-FF}. The weight functions are defined as

@@

Before introducing the WW-type approximations in the next section, 
we would like to add a comment on TMD factorization: the 
partonic description of the leading-twist structure functions in 
(\ref{Eqs:structure-functions-twist-2}) is based on factorization 
theorems \cite{Collins:1981uk,Ji:2004wu,Ji:2004xq,Collins:2011zzd,
Echevarria:2012js}. In contrast to this, the partonic description 
of the subleading-twist structure functions in 
(\ref{Eqs:structure-functions-twist-3}) is based on the
{\it assumption} that that SIDIS cross section factorizes.

In fact, a lot of progress has been achieved in recent years in the 
theoretical understanding of leading-twist observables within the TMD 
framework --- including definition, renormalization and evolution of 
leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
In contrast to this, the theory for subleading-twist TMD observables is 
only pourly developed. Still to the present day, the state-of-the-art 
approach to subleading twist TMD observables is the one of 
Refs.~\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
Bacchetta:2006tn}, 
based on a TMD tree-level formalism which we adopt here.
In fact, the results of Refs.~\cite{Metz:2004je,Gamberg:2006ru}
indicate doubts even in the tree-level formalism. 
Recently, an attempt was made to remedy these doubts \cite{Chen:2016hgw}.
Keeping in mind these ``words of warning,'' still the formulas 
(\ref{Eqs:structure-functions-twist-3}) 
are the best that theory has to offer currently. We may consider 
(\ref{Eqs:structure-functions-twist-3}) as a model itself for 
the twist-3 SIDIS observables. We hope that the phenomenological 
approach based on WW-type approximations pursued in this work might 
lead to more insight into these observables, and eventually might 
trigger more theory efforts in the future.

@@

The relations (\ref{Eq:WW-original1}--\ref{Eq:WW-original-e})
have been derived basically using operator product expansion
techniques \cite{Wandzura:1977qf,Jaffe:1991ra}. Notice that the 
operators defining $g_T^a$ and and $h_L^a$ can also be decomposed 
within the TMD framework by means of a combination of relations 
derived from the QCD equations of motion and further 
constraint relations, called Lorentz-Invariance Relations (LIRs), 
(see recent review \cite{Kanazawa:2015ajw} and references therein) 
into a twist-2 part, and dynamical twist-3 (interactions dependent) 
$\bar{q}gq$-terms and current quark mass terms.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.48\textwidth]{\FigPath/g2.pdf} 
\includegraphics[width=0.48\textwidth]{\FigPath/g2-HERMES.pdf} 
\caption{\label{Fig:g2} 
The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets. 
Left panel: data from E144 and E155 experiments at 
$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. 
Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
The estimate of the theoretical uncertainty is described in the text.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We present calculations of $g_2(x)_{\rm WW}$ in Fig.~\ref{Fig:g2}.
This result is obtained using the LO $g_1^a(x)$-parametrization 
\cite{Gluck:1998xa}. In order to display the theoretical ``uncertainty 
band'' of this WW-approximation of about $40\,\%$ as deduced in 
Ref.~\cite{Accardi:2009au} we proceed as follows: we split the 
$40\,\%$ uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
$\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
and estimate the impact of this uncertainty as 
\be\label{Eq:g2-in-WW-model-violation}
    g_2(x)_{\rm WW} = (1\pm\varepsilon_1)\frac{ d\;}{ d x}\;\Biggl[
    x\int_x^1\frac{ d y}{y} \,\biggl(
    \frac12\sum_ae_a^2\,g_1^a(y(1\pm\varepsilon_2))\biggr)\Biggr]\,.
\ee
The effect of $\varepsilon_1$ is to change the magnitude
of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
the highest measured $x$--bin.
The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
and in line with theory predictions \cite{Balla:1997hf}.
Our estimate with the splitted uncertainties 
$\varepsilon_{1,2}$ may overestimate in certain $x$--bins the 
$40\,\%$--``uncertainty band'' estimated in \cite{Accardi:2009au}. 
This however helps us to display a conservative estimate of possible 
uncertainties. 
We conclude that the WW--approximation works reasonably well, 
see Fig.~\ref{Fig:g2}.

@@

For the time being, we content ourselves with rather crude comparisons 
based on the lattice data
published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
These early works explored all nucleon and quark polarizations, but 
they used a gauge link that does not incorporate the final or initial 
state interactions present in SIDIS or Drell-Yan experiments. In other 
words, the transverse momentum dependent quantities computed in
\cite{Hagler:2009mb,Musch:2010ka} are not precisely the TMDs measurable 
in experiment. More caveats will be discussed along the way.

@@

	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{7,q} \quad \quad \\

@@

	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{10,q} \quad \quad

@@

To summarize, our procedure is to solve first the convolution 
integrals in Gaussian Ansatz, and use then WW-type approximations.
When implementing this procedure we will see that the results 
for the structure functions can be conveniently expressed in 
terms of the basis TMDs or their adequate transverse moments.

@@
